---
title: "Model Selection in Regression"
author: "YOUR NAME"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)

library(tidyverse)
library(tidymodels)
library(leaps)


set.seed(98249)
```

## Code from Lecture

```{r}
cann <- read_csv("https://www.dropbox.com/s/s2a1uoiegitupjc/cannabis_full.csv?dl=1")

cann <- cann %>%
  select(-Type, -Strain, -Effects, -Flavor, -Dry, -Mouth)

head(cann)
```

```{r}
models <- regsubsets(Rating ~ Creative + Energetic + Tingly, 
                     data = cann, method = "exhaustive")

summary(models)
```


```{r}
summary(models)$adjr2  # bigger is better
summary(models)$cp     # smaller is better
summary(models)$bic    # more negative is better
```

```{r}

models <- regsubsets(Rating ~ ., 
                     data = cann, method = "forward",
                     nvmax = 61)

summary(models)
```


```{r}
bic_scores <- summary(models)$bic
bic_scores
```

```{r, echo = FALSE}
ggplot(, aes(x = 1:61, y = bic_scores)) +
  geom_point()
```

```{r}
which.min(bic_scores)
summary(models)$outmat[13,]
```


## Try it!

#### Determine the best model via **backwards selection**.  Fit that model to the data and report results.

#### Determine the best model via **forwards selection**.  Fit that model to the data and report results.


## Regularization Code from Lecture

```{r}
lasso_spec <- linear_reg(penalty = 0.1, mixture = 1) %>%
  set_engine("glmnet") %>%
  set_mode("regression")
```


```{r}
ridge_spec <- linear_reg(penalty = 0.1, mixture = 0) %>%
  set_engine("glmnet") %>%
  set_mode("regression")
```

## Try it!

#### Fit a **LASSO** model to the cannabis data with lambda = 0.1.  Then fit one with lambda = 0.5.  What is different?

#### Fit a **Ridge Regression** model to the cannabis data with lambda = 0.1.  Then fit one with lambda = 0.5.  What is different?

#### Which model do you prefer?

#### (Bonus)  What is the best choice of lambda?

