---
title: "Variable Selection and Regularization"
author: "YOUR NAME HERE"
format: 
  html:
    code-fold: true
    code-line-numbers: true
    code-tools: true
    self-contained: true
editor: visual
execute:
  message: false
---

## Setup

Declare your libraries:

```{r}
#| label: libraries-r
#| include: false
library(tidyverse)
library(tidymodels)
library(glmnet)
library(discrim)
library(rpart)
library(rpart.plot)
library(baguette)
```


## Code from Lecture

```{r}
cann <- read_csv("https://www.dropbox.com/s/s2a1uoiegitupjc/cannabis_full.csv?dl=1")

cann <- cann %>%
  select(-Type, -Strain, -Effects, -Flavor, -Dry, -Mouth) %>%
  drop_na()

head(cann)
```


```{r}
models <- regsubsets(Rating ~ Creative + Energetic + Tingly, 
                     data = cann, method = "exhaustive")

summary(models)
```

```{r}
summary(models)$adjr2  # bigger is better
summary(models)$cp     # smaller is better
summary(models)$bic    # more negative is better
```


```{r}

models <- regsubsets(Rating ~ ., 
                     data = cann, method = "forward",
                     nvmax = 61)

summary(models)
```

```{r}
bic_scores <- summary(models)$bic
bic_scores
```

```{r}
ggplot(, aes(x = 1:61, y = bic_scores)) +
  geom_point()
```

```{r}
which.min(bic_scores)
summary(models)$outmat[13,]
```


## Try it!

#### Determine the best model via **backwards selection**. Fit that model to the data and report results.

#### Determine the best model via **forwards selection**. Fit that model to the data and report results.

## Regularization Code from Lecture

```{r}
lasso_spec <- linear_reg(penalty = 0.1, mixture = 1) %>%
  set_engine("glmnet") %>%
  set_mode("regression")
```

```{r}
ridge_spec <- linear_reg(penalty = 0.1, mixture = 0) %>%
  set_engine("glmnet") %>%
  set_mode("regression")
```


## Try it!

#### Fit a **LASSO** model to the cannabis data with lambda = 0.1. Then fit one with lambda = 0.5. What is different?

#### Fit a **Ridge Regression** model to the cannabis data with lambda = 0.1. Then fit one with lambda = 0.5. What is different?

#### Which model do you prefer?

#### (Bonus) What is the best choice of lambda?
